---
title: "Alcohol vs Seat choice"
author: "Marcia D Alarcon"
date: "14 September 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference in alcohol consumption based on where one sits in class.

$H_A$: There is a difference in alcohol consumptions based on where one sits.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The box plots shows that people in the back tend to consume more alcohol and there doesn't appear to be a difference between the ones who sit in the middle and front.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This fancy boxplotplot shows the same information as the last boxplot however the outliers were just added.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

Based on this numerical summary the ones who sit in the back consume on average 9.6 drinks, the ones in the front drink 1.8 on average, and the middle a average of 3.2 drinks.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

We have a p value of 0.000116 so we conclude that we reject the null hypothesis. There is a difference with where you sit and the alcohol that is consumed. The Tukey test shows that the confidence interval contains 0 for middle front. Meaning we have no evidence of the of any difference in alcohol consumption between the students that sit in the middle and the students that sit in the front. 

## Conclusions


