---
title: "Alcohol vs Seat choice"
author: "Marcia D Alarcon"
date: "14 September 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference in alcohol consumption based on where one sits in class.

$H_A$: There is a difference in alcohol consumptions based on where one sits.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The box plots shows that people in the back tend to consume more alcohol and there doesn't appear to be a difference bewteen the ones who sit in the middle and front.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This fancy boxplotplot shows the same information as the last boxplot however the outliers were just added.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The poepl who dit in the back have the 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is smaller than 

## Conclusions


